README

### 2017-04-10 src/README.Rmd
Update article selection based on @emdelponte
Updated to 200 articles from the journals suggested by @emdelponte in
https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/
issues/6

The top 20 journals in the discipline of plant pathology were selected according to Google Scholar's ranking by h-index, (https://scholar.google.com.au/citations?view_op=top_venues&hl=en&vq=bio_plantpathology).

100 articles are chosen at random with the assumption that journals publish an average 10 articles per issue, and using a confidence level of 95% and confidence interval of 10% we only need 88 samples, so to round it up and make it even, we'll select 100 articles over the last five years from a population that should be ~1000.

@@

set.seed(27)
```
## Import data
The list of the top 20 plant pathology journals was retrieved from Google Scholar on December 5, 2016 and saved as a CSV file for reproducibility.

```{r journal_list}
journal_list <- read.csv("../data/Google Scholar Top 20 Plant Pathology Journals 05-12-2016.csv")

journal_list[1:20, -4] # drop h-index median value
```

@@

```{r journal_sample_order}
journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```

@@

*How to handle reviews or letters?*

@@

year <- sample(2012:2016, 100, replace = TRUE)

start_page <- sample.int(150, 100)

journals <- cbind(journals, year, start_page)

journals[1:100, -1]

@@

### Check the number of articles per journal

```{r}
journals %>%  
 group_by(Publication) %>% 
    tally(sort = TRUE)

>>>>

Twenty journals in the discipline of plant pathology were selected by the authors as being the primary choice for most plant pathologists when publishing manuscripts.

Using the assumption that journals publish an average 10 articles per issue, for a population of ~1000 articles, using a confidence level of 95% and confidence interval of 10% we need 88 samples. In [Issue #3](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/issues/3), we decided to select 200 articles to have a large sample of the population.

@@

set.seed(1)
```
## Import data
The list of the top 20 plant pathology journals was retrieved from Google Scholar on December 5, 2016 and saved as a CSV file for reproducibility.

```{r journal_list}
journal_list <- tibble(
  seq(1:20),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Journal of Plant Virology",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))

names(journal_list) <- c("number", "publication")
```

@@

```{r journal_sample}
journals <- tibble(sample(1:20, 200, replace = TRUE))
names(journals) <- "number"
journals <- left_join(journals, journal_list, "number")
```

@@

@@

year <- sample(2012:2016, 200, replace = TRUE)

start_page <- sample.int(150, 200, replace = TRUE)

(journals <- cbind(journals, year, start_page)[, -1])

@@

## Check the number of articles per journal

```{r, count}
journals %>%  
 group_by(publication) %>% 
    tally(sort = TRUE) 
```

## R Session Info
```{r, session_info}
sessionInfo()
```
